draftFiguresPaper

### 2025-10-23 draftFiguresPaper.Rmd
Fig1 Fig2 v1

# 2) Build the map with integer labels and no decimals:
map_plot_viridis_clean <- ggplot() +
  geom_spatvector(
    data = world_no_antarctica,
    aes(fill = n_papers),
    color = "grey70",
    size  = 0.1
  ) +
  scale_fill_viridis_c(
    name    = "Papers",
    # option  = "plasma",
    trans   = "log10",
    breaks  = my_breaks,
    labels  = label_number(accuracy = 1,    # round to whole numbers
                           big.mark = ",",
                           trim     = TRUE),
    na.value = "grey80"
  ) +
  coord_sf(expand = FALSE) +
  labs(
    title    = "Global Publication Counts by Country",
    # subtitle = "Log₁₀ scale, viridis “plasma” palette"
  ) +
  theme_void(base_size = 14) +
  theme(
    legend.position  = "bottom",
    legend.key.width = unit(2, "cm"),
    plot.title       = element_text(face = "bold", hjust = 0.5),
    plot.subtitle    = element_text(hjust = 0.5)
  )

@@

world_countries_merged <- merge(world_countries, surveys_by_country, by.x = "adm0_a3", by.y = "iso3", all.x = T)

>>>>

# 2) Build the map with integer labels and no decimals:
map_plot_viridis_clean <- ggplot() +
  geom_spatvector(
    data = world_no_antarctica,
    aes(fill = n_papers),
    color = "grey80",
    size  = 0.1
  ) +
  scale_fill_gradientn(
    colours = c("#DCC9D2", "#8B475D", "#4F2A30"),
    name    = "Papers",
    trans   = "log10",
    breaks  = my_breaks,
    labels  = label_number(
      accuracy = 1,
      big.mark = ",",
      trim     = TRUE
    ),
    na.value = "grey90"
  ) +
  coord_sf(expand = FALSE) +
  labs(
    title    = "Global Publication Counts by Country",
    # subtitle = "Log₁₀ scale, viridis “plasma” palette"
  ) +
  theme_void(base_size = 14) +
  theme(
    legend.position  = "bottom",
    legend.key.width = unit(2, "cm"),
    plot.title       = element_text(face = "bold", hjust = 0.5),
    plot.subtitle    = element_text(hjust = 0.5)
  )

@@

# world_countries_merged <- merge(world_countries, surveys_by_country, by.x = "adm0_a3", by.y = "iso3", all.x = T)

world_countries$iso_a3 <- ifelse(world_countries$iso_a3_eh == "FRA", "FRA",
                                    ifelse(world_countries$iso_a3_eh == "NOR", "NOR", world_countries$iso_a3))

world_countries_merged <- merge(world_countries, surveys_by_country
                                , by.x = "iso_a3", by.y = "iso3", all.x = T, all.y = F)
